Project: Multi-fidelity probabilistic design framework for complex marine structures. My part is bottom up research into nonlinear extreme wave loading phenomena. \\

Topic: For now focusing on green water. \\


Literature study into green water. A lot of research into simulations has not yet been able to affordably and accurately simulate. Most previous research into the green water itself was conducted with experiments. These experiments are mostly fairly simplified representations of reality. with a static box representing a ship and regular waves. This has given a lot of insight. and five different types of green water events have been identified. It also left questions around the occurrence of green water and various green water event types. As most research has been experimental research, the problem has been scaled. However, during green water events air can be trapped. When this happens. the scaling laws are broken. This prevents the experimental data being used for large scales. Understanding the differences between the scaled and full scale results will make the experiments at model scale more useful.  \par 

These insights have led to the main goals of my research. The first focus is to get more insight into the statistics and occurrences of green water event types. This is being researched with long running experiments to obtain large data sets and many occurrences of green water. Secondly, the difference between small and large scale green water events will be investigated. This will be researched by repeating the same experiments at different scales and looking at the differences. 

